SAT Competition 2020\tnoteref{title}

### 2020-12-18 paper/main.tex
comment

\newcommand{\todo}[1]{{\color{purple}Todo: #1}}

@@

Instead of using or extending the DIMACS input format, we realize the Incremental track
by relying on the general incremental interface IPASIR (Re-entrant Incremental Solver API) 
for SAT applications~\cite{Balyo:2015:SATRace}. The idea is that we actually run the 
enclosing tool on its own benchmark and communicate with the competing SAT solver 
through this interface API. Not only does the SAT solver in this track
need to solve a sequence of related problems fast, but its answers to the early questions
may in general influence which questions will follow next.

@@

The incremental library track was first introduced in SAT~Race~2015 and 
then took place again in SAT~Competitions 2016 and 2017. 
Numerous applications, e.g., SMT solvers or SAT-based planners,
use SAT solvers incrementally, i.e., formulas are repeatedly refined between the solver calls.
In SAT~Competitions 2020, we selected a total \num{300} benchmark instances for the Incremental track
from the six applications described below.

@@

The application $\mathsf{genipabones}$ creates the dual rail encoding~\cite{Balyo:2015:SATRace} of a given formula and incrementally checks for each variable if it is a backbone variable or not~\cite{Janota:2015:Backbones}. 
For this application, we selected $50$ of the smallest and easiest satisfiable problems from previous SAT competitions.

@@

The application $\mathsf{genipaessentials}$ incrementally finds all the variables essential for the satisfiability of a given formula~\cite{Bryant:1987:Essentials} by incrementally testing each variable using the dual-rail encoded formula. 
For this application, we used the same $50$ easy satisfiable problems as in the backbone variable detection application.

\paragraph{Longest Simple Paths}

The application $\mathsf{genipalsp}$ finds the longest simple path in a graph. 
For this application, we selected $50$ instances of the smallest graphs provided by Balyo et al.~\cite{Balyo:2019:LSP}.

@@

The application $\mathsf{genipamax}$ solves partial MaxSAT problems by augmenting soft clauses with activation literals which are then input to a cardinality constraint~\cite{Philipp:2015:PBLib}. The MaxSAT problem is then solved by incrementally minimizing the bound of that cardinality constraint. 
For this application, we selected $50$ instances from MaxSAT Evaluation 2019\footnote{\url{https://maxsat-evaluations.github.io/2019/}}.

\paragraph{Quantified Boolean Formulas (QBF)}
The application $\mathsf{Ijtihad}$ is a QBF solver based on counterexample-guided expansion~\cite{Bloem:2018:QBFSAT}. For this application, we selected $50$ instances from QBF Evaluation 2019\footnote{\url{http://www.qbflib.org/qbfeval19.php}}.

\paragraph{Planning}
The application $\mathsf{Pasar}$ is a planner which is based on the principles of counter-example guided abstraction refinement (CEGAR)~\cite{Froleyks:2019:Pasar}. 
For this application, we selected $50$ SAS planning instances.

@@

@@

\subsection{On the Shoulders of Giants: The Evolution of SAT Solvers}
\label{sec:codebases}

With a few exceptions, progress in SAT solvers emerged as extensions or forks from existing code bases. 
One well-known tree of development is rooted in the Codebase of the Minisat solver by Niklas Éen and Niklas Sörenson~\cite{Niklas:2003:Minisat}. 
The most well-known fork of Minisat is the Glucose solver by Gilles Audemard and Laurent Simon~\cite{Audemard:2018:Glucose}. 
It introduced numerous implementations of successful new methods, e.g., Literal Block Distance (LBD)~\cite{Audemard:2009:Glucose}. 
The SAT solver RISS by Norbert Manthey is a successful and award winning fork of Glucose (version 2.2) in combination with the state-of-the-art preprocessor Coprocessor~\cite{Manthey:2012:Coprocessor2}.

Another successful string of development is rooted in the CoMinisatPS fork of Minisat by Chanseok Oh introducing three-tier clause-managment~\cite{Oh:2015:satunsat}. 
Maple first emerged as a series of forks submitted to SAT Competition 2016 implementing new innovative branching heuristics on top of available code-bases~\cite{Liang:2016:LRB}. 
The then award winning variant MapleCOMSPS is an implementation of the new branching heuristics Learning Rate based Branching (LRB) on top of CoMinisatPS~\cite{Liang:2016:MapleCOMSPS}. 
The next award winning derivative Maple\_LCM\_Dist in SAT Competition 2017 came with a new Learnt Clause Minimization (LCM) procedure and the new branching heuristic Distance (Dist). 
This was extended with case-based Chronological Backtracking (ChronoBT) by Ryvchin and Nadel~\cite{}, which resulted in the award winning solver Maple\_LCM\_Dist\_ChronoBT of SAT Competition 2018~\cite{}. 
Its extension MapleLCMDistChronoBT-DL with a new clause learning/forgetting heuristic Duplicate Learnts (DL)~\cite{} won SAT Race 2019. 
The success story of Maple resulted also in numerous submissions of modified Maple solvers in this competition, some of which have been successful (see Section~\ref{}).

CryptoMinisat by Mate Soos emerged as a fork of Minisat with an extension that brings special handling of xor clauses via gaussian elimination, which is especially effective when solving cryptographic instances~\cite{}. 
Today, CryptoMinisat is more of an independent code base than a Minisat fork coming with award winning individual implementations of recent SAT technology (see Section~\ref{}).

The SAT solvers of Armin Biere arguably belong to the best and most well-known independent code-bases. 
Lingeling has been around for years now and still we had competitive submissions of its parallel versions Plingeling in this competition. 
CaDiCaL came up in SAT Competition 2017 and has been award winning since then. 
Despite the fact that it seems very hard to lift the state-of-the-art with a completly new codebase, the new SAT solver Kissat by Armin Biere which was submitted for the first time this year set a new standard in sequential SAT solving in this competition (see Section~\ref{}).

ParaFrost by Osama and Wijs is another new codebase introducing several interesting new concepts~\cite{}. 
Its sequential variant was submitted for the first time in this competition.

@@

\subsubsection{CryptoMiniSat-CCAnr and CryptoMiniSat5}

>>>>

\newcommand{\todo}[1]{{\color{purple}Todo: #1}}
\newcommand{\solver}[1]{\texttt{#1}}

@@

Instead of using or extending the DIMACS input format, we realize the Incremental track
by relying on the general incremental interface IPASIR (Re-entrant Incremental Solver API) 
for SAT applications~\cite{Balyo:2015:SATRace}. The idea is that we actually run the 
enclosing tool on its own benchmark and communicate with the competing SAT solver 
through this interface API. Not only does the SAT solver in this track
need to solve a sequence of related problems fast, but its answers to the early questions
may in general influence which questions will follow next.
% E.g. Smaller unsat cores may allow the enclosing tool to converge using fewer SAT calls!

@@

The incremental library track was first introduced in SAT~Race~2015 and 
then took place again in SAT~Competitions 2016 and 2017. 
Benchmarks for the incremental track are divided into two parts: 
Applications which implement and use an incremental SAT solver in their backend and benchmark instances which serve as input to these applications. 
For evaluating the incremental library track of this competition, we used six applications which implement the IPASIR interface -- ranging from determination of backbone variables to SAT-based planning. 
For each of those applications, we individually selected $50$ problem instances serving as input for the respective application.

@@

The application \textsf{genipabones} incrementally determines backbone variables in a given satisfiable SAT instances using the dual rail encoding of the given instance~\cite{Balyo:2015:SATRace}.
Backbone variables have the same value in all models of a formula~\cite{Janota:2015:Backbones}. 
We selected $50$ of the smallest and easiest satisfiable instances from previous SAT competitions to evaluate solver performance with this application.

@@

The application \textsf{genipaessentials} incrementally determines essential variables in a given satisfiable formula~\cite{Balyo:2015:SATRace}. 
Essential variables have to be assigned in all partial models of a formula~\cite{Bryant:1987:Essentials}. 
We used the same $50$ easy satisfiable instances as in backbone detection to evaluate solver performance with this application.

\paragraph{Longest Simple Paths (LSP)}

The application \textsf{genipalsp} determines longest simple paths in a graph~\cite{Balyo:2019:LSP}. 
We selected $50$ easy LSP instances for our evaluation.\footnote{\url{http://algo2.iti.kit.edu/kalp/}}

@@

The application \textsf{genipamax} solves partial MaxSAT problems by augmenting soft clauses with activation literals which are then input to a cardinality constraint~\cite{Philipp:2015:PBLib}. 
The MaxSAT problem is then solved by incrementally minimizing the bound of that cardinality constraint. 
For this application, we selected $50$ instances from \texttt{MaxSAT Evaluation 2019}.\footnote{\url{https://maxsat-evaluations.github.io/2019/}}

\paragraph{Quantified Boolean Formulas (QBF)}
\textsf{Ijtihad} is a QBF solver which uses counter\-example-guided expansion to incrementally solve a given QBF instance with a SAT solver~\cite{Bloem:2018:QBFSAT}. 
Here we used $50$ instances from \texttt{QBF Evaluation 2019}.\footnote{\url{http://www.qbflib.org/qbfeval19.php}}

\paragraph{Planning (SAS+)}
We selected $50$ planning instances to evaluate incremental SAT solvers with \textsf{Pasar} -- a planner which uses counter\-example-guided abstraction refinement (CEGAR)~\cite{Froleyks:2019:Pasar}.

@@

\paragraph{Marginal Contributions to VBS} Interestingly, the second (Relaxed-Maple-newTech) and the third (CryptoMinisat-lsids) ranked solver both outperform the winning solver (Kissat-sat) when we project only on the instance families ``antibandwidth''~\cite{} or ``timetable''~\cite{}.

@@

\subsection{On the Shoulders of Giants: Popular Code-Bases}
\label{sec:codebases}

Progress in SAT solvers is usually recorded based on successful evaluations of  modifications of existing code-bases. 
One well-known tree of development is rooted in the code-base of \solver{Minisat} by Eén and Sörenson~\cite{Niklas:2003:Minisat}. 
A well-known fork of \solver{Minisat} is \solver{Glucose} by Audemard and Simon~\cite{Audemard:2018:Glucose}, among others introducing Literal Block Distance (LBD) for weighing clauses in forgetting heuristics~\cite{Audemard:2009:Glucose}. 
The SAT solver \solver{RISS} by Manthey is a successful and award winning fork of \solver{Glucose} in combination with the state-of-the-art preprocessor \solver{Coprocessor}~\cite{Manthey:2012:Coprocessor2}.

Another more recent string of development is rooted in the \solver{CoMinisatPS} fork of \solver{Minisat} by Chanseok Oh introducing three-tier clause-managment~\cite{Oh:2015:satunsat}. 
The SAT solver \solver{Maple} appeared as a series of forks presenting innovative branching heurstics at SAT Competition 2016~\cite{Liang:2016:LRB}. 
The then award winning variant \solver{MapleCOMSPS} is an implementation of a hybrid branching heuristic of classic Variable-State Independend Decaying Sum (VSIDS) and the new Learning-Rate based Branching (LRB) in \solver{CoMinisatPS}~\cite{Liang:2016:MapleCOMSPS}.

In SAT Competition 2017, Luo et al. integrated learnt clause minimization based on unit propagation (\solver{LCM}) in their award winning \solver{Maple\_LCM\_Dist}~\cite{Luo:2017:LCM} which also uses the new branching heuristic \solver{Distance (Dist)} in an initial solving period~\cite{Xiao:2017:MapleLCMDist}. 
Using \solver{Maple\_LCM\_Dist}, Ryvchin and Nadel successfully integrated conditional chronological backtracking (\solver{ChronoBT})~\cite{Nadel:2018:CBT}. 
They presented their award winning \solver{Maple\_LCM\_Dist\_ChronoBT} to SAT Competition~2018~\cite{Ryvchin:SC2018:MapleChronoBT}.

Kochemazov et al. improved three-tier clause-management by persting additional clauses through hash-based detection of repeatedly learned clauses and presented their award winning~\solver{MapleLCMDistChronoBT-DL} to SAT Race~2019~\cite{Kochemazov:SC2019:MapleChronoBTDL}. 
As can be seen in Table~\ref{tab:solvers-incremental}, numerous submissions to SAT Competition~2020 are forks of some recently award winning \solver{Maple} solver.

Starting as a \solver{Minisat}-fork and the integration of special xor treatment~\cite{Soos:2009:Crypto}, \solver{CryptoMinisat} by Soos continues to be a state-of-the-art and feature-rich SAT solver. 
One highlight of \solver{CryptoMinisat} is its advanced data-logging capabilities for statistical analysis of SAT solver behavior~\cite{Soos:2019:ChrystalBall}. 
In its new version~5, \solver{CryptoMinisat} has once again been award winning in SAT Competition~2020 (see Section~\ref{sec:cryptominisat}).

Many independent and award-winning code-bases can be found among the state-of-the-art SAT solvers written by Biere. 
The sequential SAT solver \solver{Lingeling} has been award winning since SAT Competition~2011 and is still competitive in its parallel version \solver{Plingeling}~\cite{Biere:2012:Lingeling}. 
As of SAT Competition~2017, \solver{CaDiCaL} by Biere is another independent award winning and structured implementation of the state-of-the-art in SAT solving. 
Its improved reimplementation \solver{Kissat} won in several of this competitions sequential tracks by a large margin~\cite{Biere:SC2020}.

The sequential variant to the new code-base \solver{ParaFrost} by Osama and Wijs was submitted for the first time in this competition and introduced several interesting new concepts~\cite{Osama:SC2020:Parafrost}.

@@

\subsubsection{CryptoMiniSat-CCAnr and CryptoMiniSat5}
\label{sec:cryptominisat}
